Buildtime Trend : What's trending in your build process

### 2015-04-02 buildtimetrend/presentation.tex
add slides about combining subprojects and Open Source license
add slide about Business plan

@@

      \item A JSON payload with build data is sent

@@

>>>>

    \frametitle{Combine subprojects}
    \item Client and service use dashboard : git submodule
    \item Client and service use library :
        \item create Python package \textit{buildtimetrend}
        \item available on \textit{pypi}
        \item install as dependency
    \frametitle{Open Source license}
    Transition from GNU General Public License (GPL) v3 to Affero GPLv3

@@

      \item a JSON payload with build data is sent

@@

    \frametitle{Business model}
      \item offering the service costs money
          \item storing the data
      \item Github inspired business model : free for Open Source, paying for private repos
      \item \href{https://keen.io}{Keen.io} offered to host data for free for Open Source projects. \textbf{Thanks, guys!}
      \item Further development with real data gathering : better feedback
